---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "man/figures/"
)
```

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/nicolasJouvin/FisherEM.svg?branch=master)](https://travis-ci.com/nicolasJouvin/FisherEM)
<!-- badges: end -->

> New version of the FisherEM package with the Bayesian Fisher EM implemented. 

## Installation

### R Package installation

#### CRAN dependencies

**FisherEM** needs the following CRAN R packages, so check that they are are installed on your computer.

```{r CRAN dependencies, eval = FALSE}
required_CRAN <- c("MASS", "elasticnet", "parallel", "ggplot2")
not_installed_CRAN <- setdiff(required_CRAN, rownames(installed.packages()))
if (length(not_installed_CRAN) > 0) install.packages(not_installed_CRAN)
```


#### Installing FisherEM

- A planned submission on CRAN in October

<!-- # ```{r package CRAN, eval = FALSE} -->
<!-- # install.packages("FisherEM") -->
<!-- # ``` -->

- For the development version, use the github install

```{r package github, eval = FALSE}
remotes::install_github("nicolasJouvin/FisherEM")
```

```{r, echo=FALSE, include=FALSE}
library(FisherEM)
```

<!-- - For a specific tagged release, use -->

<!-- ```{r package tag, eval = FALSE} -->
<!-- remotes::install_github("nicolasJouvin/FisherEM@tag_number") -->
<!-- ``` -->

## New features 

#### Simulation function

We added the script to simulate and reproduce of the BFEM chapter, 3 simulations are available.
```{r simulations, eval=FALSE}
# Chang 1983 setting
n = 300
simu = simu_bfem(n, which = "Chang1983")

# Section 4.2: 
p = 50
noise = 1
simu = simu_bfem(n = n, which = "section4.2", p = p, noise = noise)

# Section 4.3: 
snr = 3
simu = simu_bfem(n=n, which = "section4.2", snr)
```


#### The Bayesian Fisher-EM algorithm

The function structure, arguments and output are similar to `fem()`and `sfem()`.

```{r toy-example}
Y = iris[,-5]
cl_true = iris[,5]
res.bfem = bfem(Y, K = 3, model="DB", init = 'kmeans', method = 'gs', nstart = 10)

print(fem.ari(res.bfem, cl_true))
```

#### Visualisation

```{r bound-evolution}
ggbound = plot(res.bfem, type = 'elbo')
ggbound
```
```{r subspace}
ggspace = plot(res.bfem, type = 'subspace')
ggspace
```
